---
title: "Residential care chains"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

This is an analysis intended to investigate whether residential and nursing homes that are parts of chains have different assessed levels of care quality.

```{r opts}
library(knitr)
opts_chunk$set(echo = FALSE)
opts_chunk$set(include = TRUE)
opts_chunk$set(cache = FALSE)
opts_chunk$set(tidy = TRUE)
```

```{r data, message=FALSE}
library(ordinal)
library(effects)
library(ggplot2)
library(dplyr)
library(vcd)

comp11 <- read.csv('comp11.csv')
comp11$chapter1.old <- ordered(comp11$chapter1, levels = c('X', 'N','Y'))
comp11$chapter2.old <- ordered(comp11$chapter2, levels = c('X', 'N','Y'))
comp11$chapter3.old <- ordered(comp11$chapter3, levels = c('X', 'N','Y'))
comp11$chapter4.old <- ordered(comp11$chapter4, levels = c('X', 'N','Y'))
comp11$chapter5.old <- ordered(comp11$chapter5, levels = c('X', 'N','Y'))


comp11$chapter1.new <- ordered(comp11$chapter1, levels = c('I', 'R', 'G', 'O'))
comp11$chapter2.new <- ordered(comp11$chapter2, levels = c('I', 'R', 'G', 'O'))
comp11$chapter3.new <- ordered(comp11$chapter3, levels = c('I', 'R', 'G', 'O'))
comp11$chapter4.new <- ordered(comp11$chapter4, levels = c('I', 'R', 'G', 'O'))
comp11$chapter5.new <- ordered(comp11$chapter5, levels = c('I', 'R', 'G', 'O'))

comp11$chap1 <- ordered(comp11$chap1, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap2 <- ordered(comp11$chap2, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap3 <- ordered(comp11$chap3, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap4 <- ordered(comp11$chap4, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap5 <- ordered(comp11$chap5, levels = c('Inadequate', 'Poor', 'Good'))

```

```{r functions}

ef.plot <- function(m, term, title = NULL, response.name = term, conf.int = TRUE){
  # Alternative to plots produced by the effects package, using ggplot2
  require(effects)
  require(ggplot2)
  
  if (!(class(m) %in% c('polr', 'clm'))) stop('Only works for polr or clm objects')
  if (!is.character(term)) stop('term must be a string')
  
  eftabs <- effect(term, m)
  dta <- data.frame(eftabs$prob)
  dta.l <- data.frame(eftabs$lower.prob)
  dta.u <- data.frame(eftabs$upper.prob)
  names(dta) <- eftabs$y.levels
  names(dta.l) <- eftabs$y.levels
  names(dta.u) <- eftabs$y.levels
  
  dta <- suppressMessages(reshape2::melt(dta))
  dta.l <- suppressMessages(reshape2::melt(dta.l))
  dta.u <- suppressMessages(reshape2::melt(dta.u))
  
  k <- dim(eftabs$x)[1]
  n <- dim(dta)[1]
  
  if (is.null(levels(eftabs$x))){ # not a factor
    dta[, term] <- eftabs$x
  } else {
    dta[, term] <- gl(k, 1, n, labels = levels(eftabs$x[, 1]))
  }
  dta$Lower <- dta.l$value
  dta$Upper <- dta.u$value
  names(dta)[1:2] <- c(eftabs$response,'Probability')
  if (is.null(title)) title <- eftabs$response
  if (is.null(response.name)) response.name <- term
  g <- ggplot(dta, aes_string(x = term, y = "Probability", group = eftabs$response)) + 
    geom_point(colour = 'red', size = 3) +
    geom_line() + facet_grid(formula(paste(eftabs$response, "~ ."))) + theme(axis.text.x = element_text(size = 10)) + 
    theme_bw() + labs(title = title, x = response.name)
  
  if (conf.int) {
    g + geom_errorbar(aes(ymin = Lower, ymax = Upper), colour = 'darkgrey', width = 0.1) 
  } else g
    
}
```


# Using three categories of size

```{r vars}
comp11$chain.type <- ifelse(comp11$Group_Size == 1, 'Independent',
                       ifelse(comp11$Group_Size > 1 & comp11$Group_Size <= 10, 'Small',
                          ifelse(comp11$Group_Size > 10 & comp11$Group_Size <= 70, 'Medium',
                            ifelse(comp11$Group_Size > 70, 'Large', NA))))

comp11$for_profit <- ifelse(comp11$sector == 'For-Profit', 'For-Profit', 'Non-Profit')

dvs <- paste0('chap', 1:5)
dvs.old <- paste0('chapter', 1:5, '.old')
dvs.new <- paste0('chapter', 1:5, '.new')

```

## Descriptive statistics

```{r dstats1}
library(dplyr)
grps <- comp11 %>% group_by(care.home.group) %>% select(care.home.group, sector, Group_Size)

comp11 %>% group_by(sector)  %>% summarise(mean = mean(total.beds, na.rm = TRUE),
                                          median = median(Group_Size, na.rm = TRUE),
                                          max = max(Group_Size, na.rm = TRUE),
                                          sd = sd(Group_Size, na.rm = TRUE),
                                          n = n())


comp11 %>% group_by(sector, regist.type) %>% summarise(mean = mean(Group_Size, na.rm = TRUE),
                                          median = median(Group_Size, na.rm = TRUE),
                                          max = max(Group_Size, na.rm = TRUE),
                                          sd = sd(Group_Size, na.rm = TRUE),
                                          n = n())

library(vcd)
tab1 <- xtabs(~sector + chain.type, comp11)
tab1
summary(tab1)
mosaic(tab1, shade = TRUE)


ggplot(comp11, aes(x = Group_Size, colour = sector)) + geom_density()
```

# Dummy for being in a chain

```{r inchain}
comp11 <- comp11 %>% filter(sector != 'Local Authority')

forms <- paste(dvs.old, '~ sector * In_Group + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'Old', ], Hess = TRUE)

lapply(1:5, function(x) regs.old.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs.new, '~ sector * In_Group + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'New', ], Hess = TRUE)

lapply(1:5, function(x) regs.new.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs, '~ sector * In_Group + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.pop <- lapply(forms, clm, data = comp11, Hess = TRUE)

lapply(1:5, function(x) regs.all.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

lapply(regs.old.pop, summary)

lapply(regs.new.pop, summary)

lapply(regs.all.pop, summary)

```


```{r regs1}
forms <- paste(dvs.old, '~ sector*chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'Old', ], Hess = TRUE)

lapply(1:5, function(x) regs.old.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs.new, '~ sector*chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'New', ], Hess = TRUE)

lapply(1:5, function(x) regs.new.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs, '~ sector*chain.type + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.pop <- lapply(forms, clm, data = comp11, Hess = TRUE)

lapply(1:5, function(x) regs.all.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

lapply(regs.old.pop, summary)

lapply(regs.new.pop, summary)

lapply(regs.all.pop, summary)
```

Problem caused by lack of large, local authority chains.  You could argue that any local authority home has the advantage of being part of a larger group even if the LA only operates a small number of homes, so perhaps exclude them?  First, try without interactions.

```{r reg1a}
forms <- paste(dvs.old, '~ sector + chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'Old', ], Hess = TRUE)

lapply(1:5, function(x) regs.old.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs.new, '~ sector + chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.pop <- lapply(forms, clm, data = comp11[comp11$compliance_regime == 'New', ], Hess = TRUE)

lapply(1:5, function(x) regs.new.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

forms <- paste(dvs, '~ sector+ chain.type + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.pop <- lapply(forms, clm, data = comp11, Hess = TRUE)

lapply(1:5, function(x) regs.all.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

lapply(regs.old.pop, summary)

lapply(regs.new.pop, summary)

lapply(regs.all.pop, summary)

```

## Second, exclude LA homes altogether.


```{r regnola, include=FALSE}
forms <- paste(dvs.old, '~ sector * chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.pop <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'Old' & comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.old.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'Old' & comp11$sector != 'Local Authority')))

forms <- paste(dvs.new, '~ sector * chain.type + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.pop <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'New' & comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.new.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'New' & comp11$sector != 'Local Authority')))

forms <- paste(dvs, '~ sector * chain.type + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.pop <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.all.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$sector != 'Local Authority')))

lapply(regs.old.pop, summary)

lapply(regs.new.pop, summary)

lapply(regs.all.pop, summary)

```

# Continuous measure of chain size

Use log(Group_Size) because it is so skewed.

```{r reg2}
comp11$logChain_Size <- log(comp11$Group_Size)

forms <- paste(dvs.old, '~ sector * logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.pop <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'Old')

lapply(1:5, function(x) regs.old.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'Old')))

forms <- paste(dvs.new, '~ sector * logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.pop <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'New')

lapply(1:5, function(x) regs.new.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'New')))

forms <- paste(dvs, '~ sector * logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.pop <- lapply(forms, clm, data = comp11, Hess = TRUE)

lapply(1:5, function(x) regs.all.pop[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))

lapply(regs.old.pop, summary)

lapply(regs.new.pop, summary)

lapply(regs.all.pop, summary)


forms <- paste(dvs.old, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.noi <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'Old')

lapply(1:5, function(x) regs.old.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'Old')))

forms <- paste(dvs.new, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.noi <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'New')

lapply(1:5, function(x) regs.new.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'New')))

forms <- paste(dvs, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.noi <- lapply(forms, clm, data = comp11, Hess = TRUE)

lapply(1:5, function(x) regs.all.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE))


```
# LR test of interaction effects

```{r inttests}
Map(anova, regs.old.noi, regs.old.pop)

Map(anova, regs.new.noi, regs.new.pop)

Map(anova, regs.all.noi, regs.all.pop)
```
*No evidence that interactions are required*

## Effect plots for `log(Chain_Size)`.  

These plots use regressions without interactions.

```{r efplot}

lapply(regs.all.noi, ef.plot, term = 'logChain_Size')
```



## Repeat but excluding local authority homes

```{r nola}

forms <- paste(dvs.old, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m')

regs.old.noi <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'Old' & comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.old.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'Old' & comp11$sector != 'Local Authority')))

forms <- paste(dvs.new, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia + OVer.65.m  ')
regs.new.noi <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$compliance_regime == 'New' & comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.new.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$compliance_regime == 'New' & comp11$sector != 'Local Authority')))

forms <- paste(dvs, '~ sector + logChain_Size + Total.Beds.k + Age.k + purpose.built  + dementia  + OVer.65.m  ')
regs.all.noi <- lapply(forms, clm, data = comp11, Hess = TRUE, subset = comp11$sector != 'Local Authority')

lapply(1:5, function(x) regs.all.noi[[x]]$call <<- call('clm', formula = as.formula(forms[x]), data = quote(comp11), Hess = TRUE, subset = quote(comp11$sector != 'Local Authority')))

lapply(regs.all.noi, summary)

```
