---
title: "Care home chains"
output:
  html_notebook: default
  pdf_document: default
date: '2017-01-24'
---

# Introduction

The purpose of this analysis is to see if there is evidence of performance differences between care homes that are part of chains.  The hypothesis is that chains that are part of for-profit groups will have lower performance but those that are not will have higher performance because of learning benefits.

```{r setup, echo=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
opts_chunk$set(include = TRUE)
opts_chunk$set(cache = FALSE)
opts_chunk$set(tidy = TRUE)
opts_chunk$set(fig.width = 6, fig.asp = 0.618, out.width = "80%", fig.align = "center")
```

```{r data, message=TRUE, echo=FALSE}

library(ordinal)
library(effects)
library(ggeffects)
library(tidyverse)
library(modelr)
library(broom)
library(vcd)
library(stringr)
library(texreg)
library(tidyclm)

comp11 <- read_csv('C:\\Users\\dbarron\\Dropbox\\Care Homes\\comp11.csv')
comp11$chapter1.old <- ordered(comp11$chapter1, levels = c('X', 'N','Y'))
comp11$chapter2.old <- ordered(comp11$chapter2, levels = c('X', 'N','Y'))
comp11$chapter3.old <- ordered(comp11$chapter3, levels = c('X', 'N','Y'))
comp11$chapter4.old <- ordered(comp11$chapter4, levels = c('X', 'N','Y'))
comp11$chapter5.old <- ordered(comp11$chapter5, levels = c('X', 'N','Y'))


comp11$chapter1.new <- ordered(comp11$chapter1, levels = c('I', 'R', 'G', 'O'))
comp11$chapter2.new <- ordered(comp11$chapter2, levels = c('I', 'R', 'G', 'O'))
comp11$chapter3.new <- ordered(comp11$chapter3, levels = c('I', 'R', 'G', 'O'))
comp11$chapter4.new <- ordered(comp11$chapter4, levels = c('I', 'R', 'G', 'O'))
comp11$chapter5.new <- ordered(comp11$chapter5, levels = c('I', 'R', 'G', 'O'))

comp11$chap1 <- ordered(comp11$chap1, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap2 <- ordered(comp11$chap2, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap3 <- ordered(comp11$chap3, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap4 <- ordered(comp11$chap4, levels = c('Inadequate', 'Poor', 'Good'))
comp11$chap5 <- ordered(comp11$chap5, levels = c('Inadequate', 'Poor', 'Good'))

```

```{r functions, echo=FALSE}

# tidy.clm <- function (x, conf.int = FALSE, conf.level = 0.95, exponentiate = FALSE, 
#     quick = FALSE, cluster = FALSE, vcov = NULL, ...) {
#     if (quick) {
#         co <- ordinal:::coef.clm(x)
#         ret <- data.frame(term = names(co), estimate = unname(co))
#         return(process_lm(ret, x, conf.int = FALSE, exponentiate = exponentiate))
#     }
#     s <- summary(x)
#     ret <- tidy.summary.clm(s, cluster = cluster, vcov = vcov)
#     process_clm(ret, x, conf.int = conf.int, conf.level = conf.level, 
#         exponentiate = exponentiate)
# }
# 
# process_clm <- function(ret, x, conf.int = FALSE, conf.level = 0.95, exponentiate = FALSE){
#   if (exponentiate){
#     trans <- exp
#   } else {
#     trans <- identity
#   }
#   if (conf.int) {
#     CI <- suppressMessages(ordinal:::confint.clm(x, level = conf.level, type = 'Wald'))
#     colnames(CI) <- c('conf.low', 'conf.high')
#     ret <- cbind(ret, trans(unrowname(CI)))
#   }
#   ret$estimate <- trans(ret$estimate)
#   ret
# }
# 
# unrowname <- function(x){
#   rownames(x) <- NULL
#   x
# }
# 
# tidy.summary.clm <- function(x, cluster = FALSE, vcov = NULL, digits = 2, ...){
#   co <- ordinal:::coef.clm(x)
#     nn <- c("estimate", "std.error", "statistic", "p.value")
#     if (inherits(co, "listof")) {
#         ret <- plyr::ldply(co, fix_data_frame, nn[1:ncol(co[[1]])], 
#             .id = "response")
#         ret$response <- stringr::str_replace(ret$response, "Response ", 
#             "")
#     }
#     else {
#         ret <- fix_data_frame(co, nn[1:ncol(co)])
#     }
#     if (cluster){
#       if (is.matrix(vcov)) {
#         vcov <- sqrt(diag(vcov))
#       }
#       ret[, 'std.error'] <- vcov
#       ret[, 'statistic'] <- ret[, 'estimate'] / vcov
#       ret[, 'p.value'] <- pnorm(abs(ret[, 'statistic']), lower.tail = FALSE) * 2
#     }
#     ret
# }
# 
# glance.clm <- function(x, ...){
#   ret <- as.data.frame(x[c("logLik")])
#   rownames(ret) <- NULL
#   finish_glance(ret, x)
# }
# 
# get_CL_vcov<-function(model, cluster){
#   
#   require(sandwich, quietly = TRUE)
#   require(lmtest, quietly = TRUE)
#   
#   if (length(model$na.action) > 0) {
#     cluster <- cluster[-model$na.action]
#   }
#   
#   #calculate degree of freedom adjustment
#   M <- length(unique(cluster))
#   N <- length(cluster)
#   K <- length(coef(model))
#   dfc <- (M / (M - 1)) * ((N - 1) / (N - K))
#   
#   #calculate the uj's
#   uj  <- apply(estfun(model),2, function(x) tapply(x, cluster, sum))
#   
#   #use sandwich to get the var-covar matrix
#   vcovCL <- dfc * sandwich(model, meat=crossprod(uj) / N)
#   return(vcovCL)
# }
# 
# get_confint<-function(model, vcovCL){
#   t <- qt(.975,  model$df.residual)
#   ct <- coeftest(model, vcovCL)
#   est <- cbind(ct[, 1], ct[, 1] - t * ct[, 2], ct[, 1] + t * ct[, 2])
#   colnames(est) <- c("Estimate","LowerCI","UpperCI")
#   return(est)
# }


# Function to turn broom output into input to texreg.
# Just puts theshhold parameters at the end
treg_prep <- function(x){
  ix <- stringr::str_detect(x[[1]]$term, '\\|')
  k <- length(ix)
  theta <- sum(ix)
  idx <- c((theta + 1):k, 1:theta)
  map(x, ~.x[idx, ])
}


# ef.plot <- function(m, term, title = NULL, response.name = term, conf.int = TRUE, ...){
#   # Alternative to plots produced by the effects package, using ggplot2
#   require(effects)
#   require(ggplot2)
#   
#   if (!(class(m) %in% c('polr', 'clm', 'clmm'))) stop('Only works for polr or clm objects')
#   if (!is.character(term)) stop('term must be a string')
#   
#   eftabs <- effect(term, m, ...)
#   dta <- data.frame(eftabs$prob)
#   dta.l <- data.frame(eftabs$lower.prob)
#   dta.u <- data.frame(eftabs$upper.prob)
#   names(dta) <- eftabs$y.levels
#   names(dta.l) <- eftabs$y.levels
#   names(dta.u) <- eftabs$y.levels
#   
#   dta <- suppressMessages(reshape2::melt(dta))
#   dta.l <- suppressMessages(reshape2::melt(dta.l))
#   dta.u <- suppressMessages(reshape2::melt(dta.u))
#   
#   k <- dim(eftabs$x)[1]
#   n <- dim(dta)[1]
#   
#   if (is.null(levels(eftabs$x))){ # not a factor
#     dta[, term] <- eftabs$x
#   } else {
#     dta[, term] <- gl(k, 1, n, labels = levels(eftabs$x[, 1]))
#   }
#   dta$Lower <- dta.l$value
#   dta$Upper <- dta.u$value
#   names(dta)[1:2] <- c(eftabs$response,'Probability')
#   if (is.null(title)) title <- eftabs$response
#   if (is.null(response.name)) response.name <- term
#   g <- ggplot(dta, aes_string(x = term, y = "Probability", group = eftabs$response)) + 
#     geom_point(colour = 'red', size = 3) +
#     geom_line() + facet_grid(formula(paste(eftabs$response, "~ ."))) + theme(axis.text.x = element_text(size = 10)) + 
#     theme_bw() + labs(title = title, x = response.name)
#   
#   if (conf.int) {
#     g + geom_errorbar(aes(ymin = Lower, ymax = Upper), colour = 'darkgrey', width = 0.1) 
#   } else g
#     
# }
```

# Questions

1. How to define chains?
  1. Dichotomous (say, 3 or more = chain)
  1. Size groups (large, medium small)
  1. Count of number (logged?)
2. Include all homes, or just elderly?
3. Include local authority homes or not? If yes, are they chains?

# Calculate chain variables

First need to do some checking.

```{r}
comp11 %>% count(care.home.group, sort = TRUE)
```

The problem is there are 8020 cases with no `care.home.group` name.  Why?

```{r}
comp11 %>% filter(is.na(care.home.group)) %>% count(region)
```
No obvious patterns.  **Assume these homes are all independent**.  Generate a dummy `care.home.group` name for them so they don't seem to be in a chain with 8020 members!

```{r newgroup}
comp12 <- comp11 %>% 
  mutate(care.home.group.new = 
           ifelse(is.na(care.home.group), paste0('X', row_number()),
                  care.home.group))


```

Look at the care home group names to see if there are obvious problems with typos, etc. (set `eval=FALSE` so it doesn't run when file compiled.)

```{r, eval=FALSE}
comp12 %>% count(care.home.group.new) %>% View()
```
## Descriptive statistics

```{r dstats}
comp12 %>% group_by(care.home.group.new) %>% count(care.home.group.new) %>%
  summarise(mean = mean(n),
            median = median(n),
            q90 = quantile(n, probs = 0.9))
```

## Continuous

This variable is based on `care.home.group.new`. The new variable `chain_size` is calculated as the number of care homes with the same group name.

```{r cont}
comp12 <- comp12 %>% group_by(care.home.group.new) %>% 
  mutate(chain_size = n()) %>%
  ungroup()
```

Test

```{r}
comp12 %>% count(chain_size) %>%
  mutate(n_chains = n / chain_size) %>% print() %>%
  filter(chain_size > 1) %>%
  ggplot(aes(x = chain_size, y = n_chains)) + geom_col() + 
  scale_x_discrete(labels = NULL) + 
  labs(x = 'Chain size', y = 'Frequency', title = 'Chains with 2 or more members')


#  arrange(desc(n_chains), n_chains)

```

Looks OK.  Calculate `log(chain_size`)

```{r log}
comp12 <- comp12 %>%
  mutate(log_chain_size = log(chain_size))
```

```{r denplot}
comp12 %>% ggplot(aes(x = log_chain_size)) + geom_density()
```



## Dichotomous

```{r dichot}
comp12 <- comp12 %>% 
  mutate(in_chain = ifelse(chain_size >= 4, 'Yes', 'No')) 

comp12 %>%  count(in_chain)
```

## Four categories

* Independent is homes not in a chain
* Small is chains with 2-10 members
* Medium is chains with 11-70 members
* Large is chains with > 70 members

```{r}
comp12 <- comp12 %>% mutate(chain_type = ifelse(chain_size == 1, 'Independent',
                                  ifelse(chain_size <= 10, 'Small',
                                    ifelse(chain_size <= 70,  'Medium', 'Large'))))

comp12$chain_type <- forcats::fct_relevel(comp12$chain_type, levels = c('Independent', 'Small', 'Medium', 'Large'))
```


# Analysis

**Don't include local authority homes.**

```{r}
comp12.noLA <- comp12 %>% filter(sector != 'Local Authority') %>%
  mutate(sector = factor(sector))
```

## Descriptive stats

```{r}
comp12.noLA %>% 
  select(chapter1.new, chapter2.new, chapter3.new, chapter4.new, chapter5.new) %>%
  map(~table(.x, comp12.noLA$in_chain)) %>%
  map(~mosaicplot(.x, shade = TRUE))

comp12.noLA %>% count(chain_type) %>%
  ggplot(aes(x = chain_type, y = n)) +
  geom_bar(stat = 'identity') + theme_light() + 
  labs(x = 'Chain size', y = 'Frequency')
  
```

## Create formulas

```{r forms}
dvs <- paste0('chap', 1:5)
dvs.old <- paste0('chapter', 1:5, '.old')
dvs.new <- paste0('chapter', 1:5, '.new')
rhs <- ' ~ sector + Total.Beds.k + Age.years + purpose.built  + dementia  + OVer.65.m '

forms.all <- map(dvs, ~ str_c(.x, rhs)) 
forms.old <- map(dvs.old, ~ str_c(.x, rhs))
forms.new <- map(dvs.new, ~ str_c(.x, rhs))

```
## Dichotomous

```{r}
forms.new.di <- map(forms.new, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ in_chain))
fit.di <- comp12.noLA %>% 
  fit_with(clm, forms.new.di, Hess = TRUE) 

map(fit.di, tidy)
```

### Clustered standard errors

```{r}
hc.di <- fit.di %>% 
  map(get_CL_vcov, comp12.noLA$care.home.group.new) %>% 
  map(~ sqrt(diag(.x)))

op.di <- map2(fit.di, hc.di, ~ tidy(.x, cluster = TRUE, vcov = .y))

op.di <- treg_prep(op.di)
coef.nms <- c('Not-for-Profit', 'Total beds / 1000', 'Age', 'Purpose built', 'No Dementia',
              'Over 65 population (millions)', 'In a chain', 
              'I|R', 'R|G', 'G|O')
screenreg(fit.di, override.se = map(op.di, 'std.error'), 
       override.pvalues = map(op.di, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       custom.coef.names = coef.nms,
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")
```

## Interaction with sector

```{r}
forms.new.di.int <- map(forms.new.di, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ in_chain:sector))
fit.di.int <- comp12.noLA %>%
  fit_with(clm, forms.new.di.int, Hess = TRUE) 

map(fit.di.int, tidy)

```

## With clustered standard errors

```{r}
hc.di.int <- fit.di.int %>% 
  map(get_CL_vcov, comp12.noLA$care.home.group.new) %>% 
  map(~ sqrt(diag(.x)))

op.di.int <- map2(fit.di.int, hc.di.int, ~ tidy(.x, cluster = TRUE, vcov = .y))
op.di.int <- treg_prep(op.di.int)
coef.nms <- c('Not-for-Profit', 'Total beds / 1000', 'Age', 'Purpose built', 'No Dementia',
              'Over 65 population (millions)', 'In a chain', 'In chain x Not-for-profit', 
              'I|R', 'R|G', 'G|O')

screenreg(fit.di.int, override.se = map(op.di.int, 'std.error'), 
       override.pvalues = map(op.di.int, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       custom.coef.names = coef.nms,
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")

```

## Three levels of chain size

```{r}
forms.new.tri <- map(forms.new, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ chain_type))
fit.tri <- comp12.noLA %>% 
  fit_with(clm, forms.new.tri, Hess = TRUE) 

hc.tri <- map(fit.tri, ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
map2(fit.tri, hc.tri, ~tidy(.x, cluster = TRUE, vcov = .y))

```

### With interaction

```{r}
forms.new.tri.int <- map(forms.new.tri, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ chain_type:sector))
fit.tri.int <- comp12.noLA %>% 
  fit_with(clm, forms.new.tri.int, Hess = TRUE) 

hc.tri.int <- map(fit.tri.int, ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
op.tri.int <- map2(fit.tri.int, hc.tri.int, ~tidy(.x, cluster = TRUE, vcov = .y))

op.tri.int <- treg_prep(op.tri.int)

screenreg(fit.tri.int, override.se = map(op.tri.int, 'std.error'), 
          override.pvalues = map(op.tri.int, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res1",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")
```

## Continuous, logged


```{r}
forms.all.cont <- map(forms.all, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ log_chain_size))
fit.cont <- comp12.noLA %>% 
  fit_with(clm, forms.all.cont, Hess = TRUE) 

hc.cont <- map(fit.cont, ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
op.cont <- map2(fit.cont, hc.cont, ~tidy(.x, cluster = TRUE, vcov = .y))


op.cont <- treg_prep(op.cont)

screenreg(fit.cont, override.se = map(op.cont, 'std.error'), 
       override.pvalues = map(op.cont, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")
```
### With interaction

```{r}
#forms.all.cont.int <- map(forms.all.cont, ~ add_predictors(formula(.x, env = .GlobalEnv), ~ log_chain_size:sector))

forms.all.cont.int <- map(forms.all.cont, ~ add_predictors(.x, ~ log_chain_size:sector))

fit.cont.int <- comp12.noLA %>% 
  fit_with(clm, forms.all.cont.int, Hess = TRUE) 

hc.cont.int <- map(fit.cont.int, ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
op.cont.int <- map2(fit.cont.int, hc.cont.int, ~tidy(.x, cluster = TRUE, vcov = .y))
op.cont.int <- treg_prep(op.cont.int)

op.cont.int <- treg_prep(op.cont.int)

screenreg(fit.cont.int, override.se = map(op.cont.int, 'std.error'), 
       override.pvalues = map(op.cont.int, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res1",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")
```
## Effect plots

```{r, include=FALSE}
ef.plot <- function(data, ..., .model){
  require(modelr, quietly = TRUE)
  require(ggplot2, quietly = TRUE)
  
  new_data <- data_grid(data = data, ..., .model = .model)
  pred <- predict(.model, newdata = new_data)
  ret <- cbind(new_data, pred)
  ret <- gather(ret, 'Rating', 'Prediction', starts_with('fit.'))
  ret$Rating <- stringr::str_sub(ret$Rating, 5)
#  ret$Rating <- ordered(ret$Rating, levels = c('Inadequate', 'Poor', 'Good'))

  vars <- pryr::named_dots(...)

  xvar <- vars[[1]]
  if (length(vars) == 1) {
    zvar <- NULL
  } else {
    zvar <- vars[[2]]
  }  
  
  g <- ggplot(ret, aes_(x = substitute(xvar), y = quote(Prediction), 
                        group = substitute(zvar), colour = substitute(zvar))) + 
    geom_line() +
    facet_grid(~ Rating) + 
    theme(legend.position = 'top') 
  
  if (dim(ret)[1] < 100){
    print(g + geom_point())
  } else print(g)  
  
  invisible(ret)
}

clm_estimates <- function(f = forms.new, data = comp12.noLA, chn = 'log_chain_size'){
  forms <- map(f, ~ add_predictors(formula(.x, env = .GlobalEnv), formula(paste('~ ', chn))))
  fit <- fit_with(data, clm, forms, Hess = TRUE) 
  hc <- map(fit, ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
  return(list(fit = fit, formula = forms, tidyop = map2(fit, hc, ~tidy(.x, cluster = TRUE, vcov = .y))))
}
```

Need to include correct data frame in the call, and convert cml class output to polr, using the `clm.to.polr` function in the `effects` package.

```{r, message=FALSE}
edit_call <- function(x, df = quote(comp12.noLA)) {
  x$call$data <- df
  x
}

fit.tri.int.a <- map(fit.tri.int, edit_call)
fit.tri.int.b <- map(fit.tri.int.a, effects:::clm.to.polr)
fit.tri.int.pred <- map(fit.tri.int.b, ggpredict, terms = c('chain_type', 'sector'))

fit.tri.int.pred.2 <- map(fit.tri.int.pred, 
                          ~mutate(.x, response.level = 
                                    forcats::fct_relevel(.x$response.level,
                                                         'I','R','G','O')))

fit.tri.int.pred.3 <- map(fit.tri.int.pred.2, 
  ~mutate(.x, response.level = 
     recode(.x$response.level, 
                            I = 'Inadequate',
                            R = 'Requires Improvement',
                            G = 'Good',
                            O = 'Outstanding')))


ef.plot2 <- function(dta, cls = class(dta), atts = attributes(dta)){
  
  class(dta) <- cls
  attributes(dta) <- atts
  
  q <- ggeffects:::plot.ggeffects(dta) + 
    geom_line() + 
    labs(title = "", colour = "Sector") +
    xlab("Chain type") + 
    ylab("Predicted probability") +
    scale_y_continuous()
  
  plot(q)
  #invisible(q)
}

#pdf('PredProbs.pdf', onefile = FALSE, )
walk(fit.tri.int.pred.3, ef.plot2, 
    cls = class(fit.tri.int.pred[[1]]), atts = attributes(fit.tri.int.pred[[1]]))
#dev.off()
```

```{r, eval=FALSE}
#for (i in 1:5){
  ef.plot(comp12.noLA, in_chain, sector, .model = fit.di.int[[5]])
#}
```

# Estimates using only new system

## Dichotomous

```{r}
fit.di.new <- clm_estimates(chn = 'in_chain')
fit.di.new$tidyop
fit.di.new.int <- clm_estimates(chn = 'sector*in_chain')
fit.di.new.int$tidyop
```

## Three levels

```{r}
fit.tri.new <- clm_estimates(chn = 'chain_type')
fit.tri.new$tidyop
fit.tri.new.int <- clm_estimates(chn = 'sector*chain_type')
fit.tri.new.int$tidyop

fit.tri.new.int
hc.tri.new.int <- map(fit.tri.new.int[['fit']], ~ get_CL_vcov(.x, comp12.noLA$care.home.group.new))
op.tri.new.int <- map2(fit.tri.new.int[['fit']], hc.tri.new.int, ~tidy(.x, cluster = TRUE, vcov = .y))
op.tri.new.int <- treg_prep(op.tri.new.int)

op.tri.new.int <- treg_prep(op.tri.new.int)

texreg(fit.tri.new.int[['fit']], override.se = map(op.tri.new.int, 'std.error'), 
       override.pvalues = map(op.tri.new.int, 'p.value'), 
       custom.model.names = c('Safety', 'Staffing', 'Caring', 'Needs', 'Leadership'),
       stars = 0.05, dcolumn = TRUE, booktabs = TRUE, include.bic = FALSE, use.packages = FALSE,
       label = "tab:res1",
       caption = "Ordinal logistic regression results with clustered standard errors.",
       float.pos = "ht")
```

## Continuous
```{r}
fit.cont.new <- clm_estimates(chn = 'log_chain_size')
fit.cont.new$tidyop
fit.cont.new.int <- clm_estimates(chn = 'sector*log_chain_size')
fit.cont.new.int$tidyop

```

```{r, eval=FALSE}
tri.efplot.dta <- ef.plot(comp12.noLA, chain_type, sector, .model = fit.tri.new$fit[[5]])

```

```{r, eval=FALSE}
ef.plot(comp12.noLA, log_chain_size, sector, .model = fit.cont.int[[5]])
```

# Age deviation analysis

```{r agedev}
comp12.noLA.2 <- comp12.noLA %>%
  group_by(care.home.group.new) %>%
  summarise(group.mean.age = mean(Age.years, na.rm = TRUE)) %>%
  inner_join(., comp12.noLA, by = "care.home.group.new") %>%
  ungroup() %>%
  mutate(age.deviation = Age.years - group.mean.age,
         abs.age.deviation = abs(age.deviation),
         chain_type2 = forcats::fct_recode(chain_type, Small = "Independent"))
  
  
forms.new.tri.c <- map(forms.new, ~add_predictors(formula(.x, env = .GlobalEnv),
                                                  ~chain_type2 * age.deviation))
fit.tri.c <- comp12.noLA.2 %>%
  fit_with(clm, forms.new.tri.c, Hess = TRUE)

hc.tri.c <- map(fit.tri.c, ~get_CL_vcov(.x, comp12.noLA.2$care.home.group.new))
map2(fit.tri.c, hc.tri.c, ~tidy(.x, cluster = TRUE, vcov = .y))

#ef.plot(comp12.noLA.2, age.deviation, chain_type2, .model = fit.tri.c[[5]])

#map(fit.tri.c, ~ ef.plot(comp12.noLA.2, age.deviation, chain_type2, .model = .x))

```

# STAN

```{r stan, eval=FALSE}

library(rstanarm)
#comp12.noLA$total.beds.c <- comp12.noLA$Total.Beds.k * 10

stan.tri.int.1 <- stan_polr(chapter1.new ~ sector + I(Total.Beds.k * 10) + Age.years + purpose.built +
                            dementia + OVer.65.m + chain_type2 * age.deviation, data = comp12.noLA.2,
                          prior = R2(0.2, "mean"))

stan.tri.int.2 <- stan_polr(chapter2.new ~ sector + total.beds.c + Age.years + purpose.built +
                            dementia + OVer.65.m + chain_type*sector, data = comp12.noLA,
                          prior = R2(0.2, "mean"))
stan.tri.int.3 <- stan_polr(chapter3.new ~ sector + total.beds.c + Age.years + purpose.built +
                            dementia + OVer.65.m + chain_type*sector, data = comp12.noLA,
                          prior = R2(0.2, "mean"))
stan.tri.int.4 <- stan_polr(chapter4.new ~ sector + total.beds.c + Age.years + purpose.built +
                            dementia + OVer.65.m + chain_type*sector, data = comp12.noLA,
                          prior = R2(0.2, "mean"))
stan.tri.int.5b <- stan_polr(chapter5.new ~ sector + I(Total.Beds.k * 10) + Age.years + 
                               purpose.built + dementia + OVer.65.m + 
                               chain_type2 * I(age.deviation / 10), data = comp12.noLA.2,
                          prior = R2(0.7, "mean"))

summary(stan.tri.int.2)
prior_summary(stan.tri.int)
plot(stan.tri.int)
```